### 2024-10-01 Manuscript/main_ecography_R1.tex
Update main_ecography_R1.tex

\item Increasing evenness: by resampling the proportion of data (i.e. 20\%, 40\%, 60\% or 80\%) but with skewed resampling probabilities per bandwidth (i.e. an estimated number of categories summarising the distribution, like in a histogram).
Each bandwidth has an observed probability of sampling of $n$ (proportional to the number of observations in that bandwidth) and is skewed to a probability of sampling of $n \times m^{p}$. 
For bandwidths with a low density (low values of $n$) we used $m>0$ to increase their resampling probability, and the opposite for bandwidths with a high density (high values of $n$; using $m<0$ to decrease sampling property).
This effectively flattened the normal distribution of the data by some factor $p$ (here we used $p=3$).
This approximates our \textbf{competition mechanism}.
\end{itemize}

>>>>

\item Increasing evenness: by resampling the proportion of data (i.e. 20\%, 40\%, 60\% or 80\%) but with skewed resampling probabilities.
In brief, this algorithm reduces the probability of resampling observations in regions of the trait space that have many observations and increases it in regions that have few observations.
This is done by selecting of $B$ discrete categories to summarise the distribution - i.e. bandwidths - using Silverman's ``rule of thumb'' \citep[\texttt{bw.nrd0()} function in \texttt{R};][]{silverman1986density}.
Each of these discrete category $B$ has an observed probability of sampling of $b$ (the proportion of observations in the category) and each observation then gets a probability of resampling scaling with the intensity of the stressor (the proportion of what to remove $i$) of $i \times (1-b)^{p}$. 
Where $p$ is factor increasing the scaling power of the algorithm (here we used $p=3$).
In other words, observations in categories with a low density ($b<0.5$) were more likely to be resampled and the ones in categories with high density ($b>0.5$) were less likely to be resampled.
This approximates our \textbf{competition mechanism}, were observations in dense regions of the trait space are more likely to be removed than in sparse regions of the trait space.
\end{itemize}
